Appendix0\_10

### 2018-08-17 paper/Appendices/AppendixA.tex
aims and objectives
appendix C figlevel 1 CW4

\label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}

\CommentTok{# Change the data path accordingly ----------------------------------------}
\KeywordTok{setwd}\NormalTok{(}\StringTok{"/home/wangcc-me/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }\CommentTok{# in Ubuntu}
\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}

\CommentTok{# Read the data into memory -----------------------------------------------}
\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78) }\OperatorTok{==}\StringTok{ "seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the data we needed ----------------------------------------------}
\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[, }\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{7}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{55}\NormalTok{, }\DecValTok{57}\NormalTok{, }\DecValTok{58}\NormalTok{, }
    \DecValTok{59}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{61}\NormalTok{, }\DecValTok{62}\NormalTok{, }\DecValTok{63}\NormalTok{, }\DecValTok{64}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}
\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age }\OperatorTok{>=}\StringTok{ }\DecValTok{19}\NormalTok{, ]}
\KeywordTok{rm}\NormalTok{(data, data56, data78)}
\NormalTok{dfs2}

@@

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr, }\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
    \OtherTok{TRUE}\NormalTok{)]}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }
    \OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm, }\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
    \OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60} \OperatorTok{*}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN) }\OperatorTok{+}\StringTok{ }\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}
\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id, dfs2}\OperatorTok{$}\NormalTok{DayNo, dfs2}\OperatorTok{$}\NormalTok{MealMinN0), ]}
\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id))  ## number of participants = 6155}

\CommentTok{# Create a subset data with only the first observation of each}
\CommentTok{# participant --------}
\NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}

\CommentTok{# #SurveyYear :}
            \CommentTok{# Frequency Percent Cum. percent}
\CommentTok{# NDNS Year 1       801   13.01        13.01}
\CommentTok{# NDNS Year 2       812   13.19        26.21}
\CommentTok{# NDNS Year 3       782   12.71        38.91}
\CommentTok{# NDNS Year 4      1055   17.14        56.05}
\CommentTok{# NDNS Year 5       625   10.15        66.21}
\CommentTok{# NDNS Year 6       663   10.77        76.98}
\CommentTok{# NDNS Year 7       703   11.42        88.40}
\CommentTok{# NDNS Year 8       714   11.60       100.00}
  \CommentTok{# Total          6155  100.00       100.00}

\CommentTok{# create a variable combine id and day No ---------------------------------}
\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

\CommentTok{# For each subject, the total energy/carbohydrate intake for each eating }
\CommentTok{# time can be calculated --------}
\NormalTok{old <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek), }
\NormalTok{                summarise, }
                \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(EnergykJ), }
                \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
                \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg))}
\NormalTok{new <-}\StringTok{ }\KeywordTok{Sys.time}\NormalTok{() }\OperatorTok{-}\StringTok{ }\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.876385 mins}

\KeywordTok{rm}\NormalTok{(df14d, df56d, df78d, dfs2)}

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb }\OperatorTok{*}\StringTok{ }\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.26}\NormalTok{, }\FloatTok{0.75}\NormalTok{, }\DecValTok{2}\NormalTok{), }
        \DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo2 =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }
    \FloatTok{0.26}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ]  }
          \CommentTok{# some food consumption does not contain any carbohydrates}
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_carb"}\NormalTok{, }
    \StringTok{"High_carb"}\NormalTok{))}
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo2 <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo2, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Low_carb"}\NormalTok{, }\StringTok{"Med_or_high_carb"}\NormalTok{))}

\CommentTok{# Generate data sets for each day ----------------------------------------------------------}
\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }
    \StringTok{"Sex"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{, }\StringTok{"MealHourN"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{, }\StringTok{"Carbo2"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
    \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }\StringTok{"Friday"}\NormalTok{, }
        \StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

>>>>

\label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}
\linespread{0.8}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}
\CommentTok{# Change the data path accordingly ----------------------------------------}
\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}
\CommentTok{# Read the data into memory -----------------------------------------------}
\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the variables needed -------------------------------------------}
\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
\DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}

\NormalTok{dfs2 <-}\StringTok{ }\NormalTok{dfs1[dfs1}\OperatorTok{$}\NormalTok{Age}\OperatorTok{>=}\DecValTok{19}\NormalTok{,] }\CommentTok{# keep participants who aged 19 or older}
\KeywordTok{rm}\NormalTok{(data, data56, data78) }\CommentTok{# remove the unneeded big dataset}

\NormalTok{dfs2}

@@

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_chr <-}\StringTok{ }\KeywordTok{as.character}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime)}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealTime_hm <-}\StringTok{ }\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_chr,}\StringTok{" "}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }
            \OtherTok{TRUE}\NormalTok{)]}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
			\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}
\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(}\KeywordTok{strsplit}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{MealTime_hm,}
				\StringTok{":"}\NormalTok{))[}\KeywordTok{c}\NormalTok{(}\OtherTok{FALSE}\NormalTok{, }\OtherTok{TRUE}\NormalTok{, }\OtherTok{FALSE}\NormalTok{)])}

\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN0 <-}\StringTok{ }\NormalTok{(}\DecValTok{60}\OperatorTok{*}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealHourN)}\OperatorTok{+}\NormalTok{dfs2}\OperatorTok{$}\NormalTok{MealMinN}

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs2[}\KeywordTok{order}\NormalTok{(dfs2}\OperatorTok{$}\NormalTok{id,dfs2}\OperatorTok{$}\NormalTok{DayNo,dfs2}\OperatorTok{$}\NormalTok{MealMinN0),]}

\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id)) ## number of participants = 6155}

\CommentTok{# Create a subset data with only the first observation of each participant --------}

\NormalTok{NDNS <-}\StringTok{ }\NormalTok{dfs3[}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(dfs3}\OperatorTok{$}\NormalTok{id), ]}
\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(SurveyYear, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

				\begin{verbatim}
				# #SurveyYear : 
				#             Frequency Percent Cum. percent
				# NDNS Year 1       801   13.01        13.01
				# NDNS Year 2       812   13.19        26.21
				# NDNS Year 3       782   12.71        38.91
				# NDNS Year 4      1055   17.14        56.05
				# NDNS Year 5       625   10.15        66.21
				# NDNS Year 6       663   10.77        76.98
				# NDNS Year 7       703   11.42        88.40
				# NDNS Year 8       714   11.60       100.00
				#   Total          6155  100.00       100.00
				\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# how many men and women --------------------------------------------------}

\KeywordTok{with}\NormalTok{(NDNS, }\KeywordTok{tab1}\NormalTok{(Sex, }\DataTypeTok{graph =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{decimal =} \DecValTok{2}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

				\begin{verbatim}
				# Sex : 
				#          Frequency Percent Cum. percent
				# 1            2537   41.22        41.22 Men
				# 2            3618   58.78       100.00 Women
				#   Total      6155  100.00       100.00
				\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# create a variable combine id and day No ---------------------------------}

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# eating time can be calculated --------}

\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(dfs3, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                        DiaryDaysCompleted, MealHourN, DayofWeek),  }
\NormalTok{                summarise, }\DataTypeTok{Tot_Energ =}\KeywordTok{sum}\NormalTok{(EnergykJ), }
                    \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Carbohydrateg), }
                    \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Totalsugarsg), }
                    \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Starchg), }
                    \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Englystfibreg),}
                    \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Fatg), }
                    \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Proteing), }
                    \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Alcoholg), }
                    \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Nonmilkextrinsicsugarsg))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 6.429822 min}

\CommentTok{# reset the time intervals into time slots --------------------------------}

\NormalTok{### Breakfast:       6am to 9am}
\NormalTok{### morning snack:   9am to 12noon}
\NormalTok{### lunch:           12noon to 2pm}
\NormalTok{### afternoon snack: 2pm to 5pm}
\NormalTok{### dinner:          5pm to 8pm}
\NormalTok{### night snack:     8pm to 10pm}
\NormalTok{### midnight:        10pm to 6am}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
				\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# time slot can be calculated --------}
\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
\NormalTok{                summarise, }
              \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
              \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
              \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
              \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
              \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
              \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
              \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
              \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
              \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.74195 mins }

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}

\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
\CommentTok{# with 0 energy intake }
\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}	
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}

\NormalTok{vecid<-}\KeywordTok{unique}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{id)}

\CommentTok{# Filter the data by observation day--------------------------------------------}
